\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex
Update protein split part

\subsection{Evaluation and metrics}

\todo[inline]{First part is not about evaluation but optimization
  objectives, should go in the Model section:}
As the number of drug-targets are sparsely given w.r.t.\todo{no
  acronyms} to the number of both drugs and proteins considered, the
resulting training, validation and testing datasets are highly
imbalanced. As there are only $~22.000$\todo{exact number} links in
the considered subset the ratio
\begin{equation*}
	\frac{\#dti\_links}{\#drugs \cdot \#proteins} \approx 360,
\end{equation*}
consequently needing compensation in the computed loss function and
appropriate metrics for the evaluation.

Therefore, we weighted all positive drug-protein pair samples with
this ratio by introducing the following loss function w.r.t.\todo{no
  acronym} to binary cross-entropy:
\begin{equation}
	l(x,y) = - w \left[ y \cdot \log x + (1 - y) \cdot \log (1 - x) \right]
\end{equation}
for given prediction $x$ and target $y$. We average this loss among
all drug-protein pairs in the training set, leading to a stable
environment for the used optimizing scheme \textit{Adam}
\citep{Adam2014}. We implemented a 5-fold cross validation among the
proteins as justified in the results section. Furthermore, we used
early stopping to detect plateaus in the training process.

\todo[inline]{This needs to be more elaborate: add the micro- vs
  macro-averages here (formulas)}
To assess each model, we computed the \textit{area under receiver
  operating characteristic}-score (AUROC), \textit{F1-score} (F1) and
\textit{Matthews correlation coefficient} (MCC) for each considered
hyperparameter configuration setting.

\todo[inline]{Remove from here:}
Avoiding validation overfitting, we eventually tested the best
performing model on the Yamanishi dataset as presented and
discussed. Furthermore, we compare our results on this very dataset
with various other cutting edge approaches to DTI-prediction.

\subsection{Model}

\todo[inline]{Introduce the notion of top-down and bottom-up:}
In order to build a method that incorporates both top-down and
bottom-up features, we first created a model for each
individually. Hence, we assemble rich molecular structure based
features for drugs from
\textit{SmilesTransformer} \citep{SmilesTransformer} and proteins from
\textit{DeepGOPlus} \citep{DeepGoPlus}. \textit{SmilesTransformer}
introduces an autoencoder, learning over the SMILES strings and thus
the molecular organization of each drug in an unsupervised manner. On
the other hand, we take advantage of the pretrained models of
\textit{DeepGOPlus}, obtaining features from the proteins amino acid
sequence, showing significant performance in the field of protein
function prediction. Thus, both embeddings seem to suitably supplement
the following ontology based representations.

In the top-down section, we used \textit{DL2vec} \citep{DL2vec2020} to
obtain ontology based representations. DL2vec constructs a graph by
introducing vertices and edges for each ontology class and axiom,
respectively, followed by random walks starting from each
entity. These walks are eventually learned on using a Word2vec
\citep{Word2vec2013} model. Thus, we pick up rich, neighbourhood
focused representations for each entity, which has shown great results
for representing protein function and phenotypes. The overall
structure of the ontology can be seen in Figure~\ref{fig:Onto}.

@@

As we wanted to learn from the similarity of drug side effects and
protein phenotypes we opted for a deep siamese network approach, hence
learning a high-dimensional embedding emphasizing this identity by
forcing a maximal cosine similarity between these embeddings. On the
other hand we built a deep neural network for the molecular structure
based features, also benefiting from the siamese network
architecture. Therefore, the precomputed embeddings are run through a
deep neural network transformation (DNNT) which also reduces the
eventual representation size for drugs and proteins separately. An
example structure for both types of features can be found in
Figure~\ref{fig:SiameseNetwork}.

@@

\subsubsection{Graph convolutional layers}
These molecular and ontology based sub-models were added to a larger
graph convolutional model, based on the protein-protein interaction
(PPI) graph. The PPI dataset is represented by a graph $G=(V,E)$,
where each protein is represented by a vertex $v\in V$, and each edge
$e\in E\subseteq V\times V$ symbolizes an interaction between two
proteins. Additionally, we introduce mapping
$x:V\rightarrow\mathbb{R}^{d}$ projecting each vertex $v$ to its node
feature $x_v = x(v)$, where $d$ denotes the dimensionality of the node
features.

As described before, graph convolution has shown significant
performance increase in a variety of tasks. While there are various
methods out there we will only introduce the most basic one here. A
graph convolutional layer \citet{GCNConv} consists of a
learnable weight matrix followed by an aggregation step, formalized by
\begin{equation}
	\mathbf{X}^{\prime} = \mathbf{\hat{D}}^{-1/2} \mathbf{\hat{A}}
	\mathbf{\hat{D}}^{-1/2} \mathbf{X} \mathbf{\Theta}
\end{equation}
where for a given graph $G=(V,E)$, $\hat{A} = A + I$ denotes the
adjacency matrix with added self-loops for each vertex, $D$ is
described by $\hat{D}_{ii} = \sum_{j=0} \hat{A}_{ij}$, a diagonal
matrix displaying the degree of each node, and $\Theta$ denotes the
learnable weight matrix. Added self-loops enforce that each node
representation is directly dependent on its own preceding
one. Notably, the number of graph convolutional layers stacked equals
the radius of relevant nodes for each vertex within the graph.

The update rule for each individual node is
\begin{equation}
	\mathbf{x}^{\prime}_i = \mathbf{\Theta} \sum^{N}_{j}
	\frac{1}{\sqrt{\hat{d}_j \hat{d}_i}} \mathbf{x}_j
\end{equation}
where both $\hat{d}_i, \hat{d}_j$ are dependent on the edge weights
$e_{ij}$ of the graph. With simple, single-valued edge weights such as
$e_{ij}=1 \text{ }\forall (i,j)\in E$, all $\hat{d}_i$ reduce to
$d_i$, i.e., the degree of each vertex $i$. We denote this type of
graph convolutional neural layers with \textsc{GCNConv}.

While in this initial formulation the node-wise update step is defined
by the sum over all neighbouring node representations, we are able to
alter this formulation to another message passing scheme.  We are able
to rearrange the order of activation function $\sigma$, aggregation
$\mathrm{AGG}$ and linear neural layer $\mathrm{MLP}$ with this
formulation as proposed by \citet{GENConv2020}:
\begin{equation}
	\mathbf{x}_i^{\prime} = \mathrm{MLP} \left( \mathbf{x}_i +
	\mathrm{AGG} \left( \left\{
	\mathrm{\sigma} \left( \mathbf{x}_j + \mathbf{e_{ji}} \right) +\epsilon
	: j \in \mathcal{N}(i) \right\} \right)
	\right)
\end{equation}
where we will generally only consider
$\sigma \in \{\mathrm{ReLU}, \mathrm{LeakyReLU}\}$. We will denote
this generalized layer type as \textsc{GENConv}, following the
notation of \citet{PytorchGeometric}.  While the reordering is mainly
import for numerical stability, this alteration also addresses the
vanishing gradient problem for deeper convolutional networks
\cite{GENConv2020}. Additionally, we can also generalize the
aggregation function to allow different weighting functions such as
learnable $\mathrm{SoftMax}$ or $\mathrm{Power}$ for the incoming
signals for each vertex, substituting the averaging step in
\textsc{GCNConv}. Hence, while \textsc{GCNConv} suffers from both
vanishing gradients and signal fading for large scale, highly
connected graphs, each propagation step in \textsc{GENConv} emphasizes
signals with values close to $0$ and $1$. The same convolutional
filter and weight matrix are applied to and learned for all nodes
simultaneously, and the resulting information\todo{Which information?
  Specify} hold no information on their own connectivity.

@@

We employ another mechanism to avoid redundancy and fading signals in
stacked graph convolutional networks, which was introduced by
\citet{DeepGCN2019} and refined in \citet{DeeperGCN2020}. The authors
propose a residual network architecture and normalization scheme. This
structure is depicted in Figure~\ref{fig:ResGraphConvBlocks} resulting
in reusable residual blocks, which can be stacked multiple times,
thereby not losing focus of each node neighbourhood.

\subsubsection{Hyperparameter tuning}
To find the best hyperparameter configuration for the proposed model
we performed a grid search to find the most expressive and
non-redundant representation. We pretrained the bottom-up and the
top-down model separately and aimed at best performing models
w.r.t. previously described metrics. We optimized embedding sizes,
depth of the neural network, optimizer, learning rate and layer types
using an extensive, manual grid search. \todo[inline]{Specify range of
  values searched here; even better if you have the intermediate
  results and can put them here (better: in the supplement).}

@@

\subsection{Choosing a cross-validation splitting scheme}

% As in machine learning inference is derived from the underlying data,
% models and data are naturally and intrinsically linked. Thus, the more
% we understand about the pitfalls and biases within the data, the more
% we can try to bypass these difficulties. We will hereby abbreviate,
% e.g., a cross validation splitting scheme as \glqq split\grqq{}
% determining the train, validation and test subset of a given dataset.

Within DTI prediction, one can observe basic biases resulting from the
underlying datasets \citep{Pahikkala2014}. First, novel drugs are
often designed by altering non-functional components of a drug,
leading to two and more very similar drugs designed to target the same
proteins \cite{Overington2006}. This can lead to a bias when it leads
to \glqq hidden duplicates\grqq{} that can distribute among the
train--test split, resulting in a better (measured) predictive
performance than would be expected when the model is applied to
genuinely unknown interactions. Second, some proteins (which we will
denote as \textit{hub proteins}) have significantly more known
interactions with drugs than others. In the STITCH database, $5\%$
of the proteins have $40\%$ of the interactions, and similar
distributions are present in the Yamanishi and Drugbank datasets
\cite{Drugbank2007, Drugbank2017} datasets; preferentially predicting
these proteins can often increase predictive performance while again
not reflecting the actual performance when applied to a new protein
(e.g., a protein for which no interactions are known). This bias in
the number of drugs targeting certain proteins may be the result of
study bias where more \glqq valuable\grqq{} proteins have more drugs
designed to target them due to their involvement in more common
diseases (or diseases for which drugs can be more profitably
marketed).

The aim of \name is to predict candidate drugs that target a given
protein; the challenge is to develop a training and evaluation scheme
that does not simply overfit to the inherent biases in training and
testing data.

In general, when concerning cross-validation splitting schemes for DTI prediction, there are the following three options:
\begin{enumerate}
	\item Build split over drugs
	\item Build split over drug-target pairs
	\item Build split over proteins
\end{enumerate}
where the first and third option concern splitting drugs and proteins, respectively, into train, validation and test sets, and arranging the corresponding drug-target interactions. Hereby, different training and prediction schemes lead to divergent expressiveness of the resulting model. \\
The most common scheme for DTI prediction is the split over drug-target pairs \citep{Survey2018}, where likely all drugs and targets of the validation and testing phase have already occurred in the training phase, as part of other drug-target pairs. Thus, the first and second splitting scheme are exposed to the first dataset bias and are hence more likely vulnerable to transductive inference by just predicting recently seen structures, rather than implementing inductive inference and generalizing over the drug representations. Second, these two strategies are more susceptible to the second and third bias, as only in these cases the model may overfit on the number of existing interactions, while in the third scheme the number of interactions of the test proteins is not known. \\

Considering the publications of the last

In general, drug-target interaction prediction is the task of accurately predicting, whether for a given drug and a given protein there is a biological interaction within the target organism. Hereby, different training and prediction schemes lead to divergent expressiveness of the resulting model. However, when building the train-test split over compound-protein pairs for building the actual model, there are the following three options:

\todo[inline]{Relate these to the issues listed above:}
\begin{enumerate}
	\item Build split over drugs
	\item Build split over drug-target pairs
	\item Build split over proteins
\end{enumerate} 
In general, recent works do perform their split over the drugs or drug-target pairs (\cite{Survey2018}, CITATION). As there are hopefully many more drugs to discover, the drug split scheme both emphasizes the drug repurposing idea, by applying unseen compounds to existing targets, but also benefits from more complicated drug representations, leading to tremendous\todo{???} results. This performance gain is based on minor variations among large groups of pharmaceuticals, that are easy to acquire\todo{evidence}. The second scheme has knowledge on all drugs and all proteins, and is thus prone to overfitting and the same development bias. Eventually, as there only limited drug-targets \citep{Overington2006}, predicting per protein is rather counter-intuitive. As it is hard to generalize over proteins representations, we aim at reaching similar performances for both drug and protein splitting schemes. \\

In general, recent works do perform their split over the drugs or drug-target pairs (\cite{Survey2018}, CITATION). The first is more relevant for novel drugs, as it is much more likely to test a new compound than a innovative protein. However, it lies in the very nature of the used datasets, making the prediction for new drugs much easier. Thus, drugs are often built by minor variations of existing drugs, thus leading to no deviations in the functional group of that very compound (CITATION/EXAMPLE). When distributed over both train and test split, the models do not perform inductive inference and generalize, but rather implement transductive inference by just predicting the recently seen structures. Hence, when entirely new molecules are seen, the models perform much worse

The same applies to splits of drug-target pairs, as all drugs were already seen, and novelty cannot be coped with.

As mentioned in the introduction it is quite difficult to learn suitable features from proteins. In general, attempts search for motifs in the protein sequences under usage of convolutional neural networks and filters, which is more suitable for tasks like protein function prediction, than for for drug-target interaction prediction, and lack a more in-depth hypothesis on the protein side, while investing in refined drug features. \\
Thus, building splitting over proteins is the most challenging of the three options. \\

@@

This scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and molecular drug composition, and their respective observable characteristics.

>>>>

\subsection{Evaluation and metrics}
As the number of drug-targets are sparsely given w.r.t. to the number of both drugs and proteins considered, the resulting training, validation and testing datasets are highly imbalanced. As there are only $~22.000$ links in the considered subset the ratio
\begin{equation*}
	\frac{\#drugs \cdot \#proteins}{\#dti\_links} \approx 360,
\end{equation*}

consequently needing compensation in the computed loss function and appropriate metrics for the evaluation.\\

On that account, we weighted all positive drug-protein pair samples with this ratio by introducing the following loss function w.r.t. to binary cross-entropy:
\begin{equation}
	l(x,y) = - w \left[ y \cdot \log x + (1 - y) \cdot \log (1 - x) \right]
\end{equation}
for given prediction $x$ and target $y$. We average this loss among all drug-protein pairs in the training set, leading to a stable environment for the used optimizing scheme \textit{Adam} \citep{Adam2014}. We implemented a 5-fold cross validation among the proteins as justified in the results section. Furthermore, we  used early stopping to detect plateaus in the training process. \\

To assess each model, we computed the \textit{area under receiver operating characteristic}-score (AUROC), \textit{F1-score} (F1) and \textit{Matthews correlation coefficient} (MCC) for each considered hyperparameter configuration setting.\\

Avoiding validation overfitting, we eventually tested the best performing model on the Yamanishi dataset as presented and discussed. Furthermore, we compare our results on this very dataset with various other cutting edge approaches to DTI-prediction.\\

\subsection{Model}
In order to build a method that incorporates both top-down and bottom-up features, we first created a model for each individually. Hence, we assemble rich molecular structure based features for drugs from \textit{SmilesTransformer}\citep{SmilesTransformer} and proteins from \textit{DeepGOPlus}\citep{DeepGoPlus}. \textit{SmilesTransformer} introduces an autoencoder, learning over the SMILES strings and thus the molecular organization of each drug in an unsupervised manner. On the other hand, we take advantage of the pretrained models of \textit{DeepGOPlus}, obtaining features from the proteins amino acid sequence, showing significant performance in the field of protein function prediction. Thus, both embeddings seem to suitably supplement the  following ontology based represenations.\\

In the top-down section, we used \textit{DL2vec}\citep{DL2vec2020} to obtain ontology based representations. Hereby, DL2vec constructs a graph by introducing vertices and edges for each ontology class and axiom, respectively, followed by random walks starting from each entity. These walks are eventually learned on using a Word2vec \citep{Word2vec2013} model. Thus, we pick up rich, neighbourhood focused representations for each entity, which has shown great results for representing protein function and phenotypes. The overall structure of the ontology can be seen in Figure~\ref{fig:Onto}.\\

@@

As we wanted to learn from the similarity of drug side effects and protein phenotypes we opted for a deep siamese network approach, hence learning a high-dimensional embedding emphasizing this identity by forcing a maximal cosine similarity between these embeddings. On the other hand we built a deep neural network for the molecular structure based features, also benefiting from the siamese network architecture. Therefore, the precomputed embeddings are run through a deep neural network transformation (DNNT) which also reduces the eventual representation size for drugs and proteins separately. An example structure for both types of features can be found in Figure~\ref{fig:SiameseNetwork}.\\

@@

\subsubsection{Graph convolutional layers}
These molecular and ontology based sub-models were added to a larger graph convolutional model, based on the protein-protein interaction (PPI) graph. The PPI dataset is represented by a graph $G=(V,E)$, where each protein is represented by a vertex $v\in V$, and each edge $e\in E\subseteq V\times V$ symbolizes an interaction between two proteins. Additionally, we introduce mapping $x:V\rightarrow\mathbb{R}^{d}$ projecting each vertex $v$ to its node feature $x_v = x(v)$, where $d$ denotes the dimensionality of the node features. \\

As described before, graph convolution has shown significant performance increase in a variety of tasks. While there are various methods out there we will only introduce the most basic one here. A graph convolutional layer w.r.t. \citet{GCNConv} hereby consists of a learnable weight matrix followed by an aggregation step, formalized by

\begin{equation}
	\mathbf{X}^{\prime} = \mathbf{\hat{D}}^{-1/2} \mathbf{\hat{A}}
	\mathbf{\hat{D}}^{-1/2} \mathbf{X} \mathbf{\Theta}
\end{equation}

where for a given graph $G=(V,E)$, $\hat{A} = A + I$ denotes the adjacency matrix with added self-loops for each vertex, $D$ is described by $\hat{D}_{ii} = \sum_{j=0} \hat{A}_{ij}$, a diagonal matrix displaying the degree of each node, and $\Theta$ denotes the learnable weight matrix. Added self-loops enforce that each node representation is directly dependent on its own preceding one. Notably, the number of graph convolutional layers stacked equals the radius of relevant nodes for each vertex within the graph. \\

The update rule for each individual node is denoted by

\begin{equation}
	\mathbf{x}^{\prime}_i = \mathbf{\Theta} \sum^{N}_{j}
	\frac{1}{\sqrt{\hat{d}_j \hat{d}_i}} \mathbf{x}_j
\end{equation}

where both $\hat{d}_i, \hat{d}_j$ are dependent on the edge weights $e_{ij}$ of the graph. With simple, single valued edge weights such as $e_{ij}=1 \text{ }\forall (i,j)\in E$, all $\hat{d}_i$ reduce to $d_i$, i.e. the degree of each vertex $i$. We will denote this type of graph convolutional neural layers with \textsc{GCNConv}. \\

While in this initial formulation the node-wise update step is defined by the sum over all neighbouring node representations, we are able to alter this formulation for a more sophisticated message passing scheme. As described we are able to rearrange the order of activation function $\sigma$, aggregation $\mathrm{AGG}$ and linear neural layer $\mathrm{MLP}$ with this formulation as proposed by \citet{GENConv2020}:

\begin{equation}
	\mathbf{x}_i^{\prime} = \mathrm{MLP} \left( \mathbf{x}_i +
	\mathrm{AGG} \left( \left\{
	\mathrm{\sigma} \left( \mathbf{x}_j + \mathbf{e_{ji}} \right) +\epsilon
	: j \in \mathcal{N}(i) \right\} \right)
	\right)
\end{equation}

where we will generally only consider $\sigma \in \{\mathrm{ReLU}, \mathrm{LeakyReLU}\}$. We will denote this generalized layer type as \textsc{GENConv}, following the notation of \citet{PytorchGeometric}.
While the reordering is merely import for numerical stability, the authors claim that this alteration of the original formulation eases the vanishing gradient problem for deeper convolutional networks. Additionally, the authors revise the aggregation function by generalizing it, allowing more sophisticated weighting functions such as learnable $\mathrm{SoftMax}$ or $\mathrm{Power}$ for the incoming signals for each vertex, substituting the previously mentioned averaging step. Hence, while \textsc{GCNConv} suffers from both vanishing gradients and signal fading for large scale, highly connected graphs, each propagation step in \textsc{GENConv} emphasizes strong signals with values close to $0$ and $1$. Note particularly, that the same convolutional filter and weight matrix are applied to and learned for all nodes simultaneously. Note additionally, that the resulting information hold no information on their own connectivity.\\

@@

We employ another mechanism to avoid redundancy and fading signals in stacked graph convolutional networks, which was introduced by \citet{DeepGCN2019} and refined in \citet{DeeperGCN2020}. The authors propose a residual network architecture and normalization scheme, solving these issues in a variety of graph predicting tasks. This structure is depicted in Figure~\ref{fig:ResGraphConvBlocks} resulting in reusable residual blocks, which can be stacked multiple times, thereby not losing focus of each node neighbourhood. \\

\subsubsection{Hyperparameter tuning}
To find the best hyperparameter configuration for the proposed model we performed a grid search, to find the most expressive and non-redundant representation. Therefor, we pretrained the bottom-up and the top-down model separately and aimed at best performing models w.r.t. previously described metrics. Embedding sizes, depth of the neural network, optimizer, learning rate and layer types were found from an extensive, manual grid search.

@@

\subsection{Choosing a cross-validation splitting scheme}
As in machine learning inference is derived from the underlying data, models and data are naturally and intrinsically linked. Thus, the more we understand about the pitfalls and biases within the data, the more we can try to bypass these difficulties. We will hereby abbreviate, e.g., a cross validation splitting scheme as \glqq split\grqq{} determining the train, validation and test subset of a given dataset. \\
Especially within DTI prediction, one can observe elemental and basic skews \citep{Pahikkala2014}. (1.) Frequently, novel drugs are designed by altering non-functional components of a drug, leading to two and more very similar drugs, designed to target the same proteins (\textbf{CITATION?}). This bias can lead to \glqq hidden duplicates\grqq{} that can distribute among the train-test split, skewing the ultimate predictive performance. (2.) Additionally, within the realm of DTI prediction, some proteins, which we will denote as \textit{hub proteins}, have significantly more known interactions with drugs than others. In the considered subset of STITCH database, $5\%$ of the proteins had $40\%$ of the interactions, with similar biases for Yamanishi and Drugbank (\citet{Drugbank2007} and \citet{Drugbank2017}) datasets, making them easy and reliable predictors. (3.) The second distortion could be based on a publication bias for more \glqq valuable\grqq{} proteins due to their disease involvement, such as e.g., cancer, leading to more research and eventually more interacting drugs regarding those. Thus if we aim to find a drug for a given protein, the challenge is to develop a training and evaluation scheme, that does not simply overfit to those biases.\\

In general, when concerning cross-validation splitting schemes for DTI prediction, there are the following three options:
\begin{enumerate}
	\item Build split over drugs
	\item Build split over drug-target pairs
	\item Build split over proteins
\end{enumerate}
where the first and third option concern splitting drugs and proteins, respectively, into train, validation and test sets, and arranging the corresponding drug-target interactions. Hereby, different training and prediction schemes lead to divergent expressiveness of the resulting model. \\
The most common scheme for DTI prediction is the split over drug-target pairs \citep{Survey2018}, where likely all drugs and targets of the validation and testing phase have already occurred in the training phase, as part of other drug-target pairs. The second most prevalent arrangement is the split over drugs, while only close to none is aiming on a protein split.  However, the first and second splitting scheme are exposed to the first dataset bias and are hence more likely vulnerable to transductive inference by just predicting recently seen structures, rather than implementing inductive inference and generalizing over the drug representations. Second, these two strategies are more susceptible to the second and third bias, as only in these cases the model may overfit on the number of existing interactions for a single protein, while in the third scheme the number of interactions of the test proteins is not known.

Assuming a hypothetical, perfectly generalizing model built upon an unbiased dataset, this very model would yield similar performances for all three splitting schemes, not overfitting on the known structures. On the other hand, for a hypothetical entirely overfitting model, trained on a highly biased dataset, this model would show substantial deviations from the original performance over another split. \\
We emphasize, that all real-world models are prone to some sort of overfitting, and unknown, deviant entities in both validation and testing set will likely lead to some sort of performance gap for relevant metrics. However, a large disparity may hint the biases stated above.

Hence, we will perform a cross-validation over proteins for the training and prediction phase of our model, despite predicting per protein is rather counter-intuitive as there only limited drug-targets \citep{Overington2006}, and thus novel drugs are more likely to arise than novel targets. Yet, we aim to find all interacting drugs for existing targets motivating our split choice even further.

\subsection{MicroAUC}
Continuing this line, we propose the well known metric \textit{MicroAUC} for a better evaluation for this purpose. For given lists $D, P$ of drugs and proteins, respectively, and a set of known interactions $Int := \{(d_i, p_i) \}$, \textit{MicroAUC} is calculated as the average per entity (macro) \textit{AUROC} score. With respect to proteins, this can be formalized for given labels and prediction $l,y:D\times P \rightarrow \{0,1\}$  as 
\begin{equation*}
	MicroAUC_p := \underset{p\in P}{mean}\left(\left\{ \text{AUROC}(\{ (l(d_i, p), y(d_i,p))| d_i\in D\}) \right\}\right)
\end{equation*}

Note that drugs and proteins can be interchanged in this formulation, which we will denote with $MicroAUC_p$ and $MicroAUC_d$, respectively. As we want to evaluate the models performance to find all suitable drugs for each protein individually, \textit{$MicroAUC_p$} seems to be more reasonable in comparison to both $MicroAUC_d$ and $AUROC$ with respect to the previously proposed protein split cross-validation. Furthermore,

@@

This scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and molecular drug composition, and their respective observable characteristics. \\
